### 2023-02-07 README.Rmd
Update README to reflect #17 and #14 [no ci]

## Using alternative Rocker images

@@

>>>>

### Caching R packages

One can also cache (or archive) the R packages from CRAN at the time `dockerize` is executed. The cached R packages will then transfer to the container. Please note that system requirements (i.e. `deb` packages) are not cached.

```r
dockerize(graph, "~/rocker_test", cache = TRUE)
```

### Using alternative Rocker images

@@

## Recreate the computational environment for R < 3.1.0

`gran` can still be used to recreate computational environments for R < 3.1.0. The Dockerfile generated is based on Debian Woody (3.0) and the requested version of R is compiled from source. As of writing, this method works for R < 3.1.0 but not R < 2.1.0. The `image` parameter is ignored in this case.

```r
gran_rio <- resolve("rio", snapshot_date = "2013-08-28") ## R 3.0.1
dockerize(gran_rio, output_dir = "~/old_renviron")
```
